method

### 2022-01-27 06_Paper/ER-ED/method.Rmd
restructured R chucks
added questionnaire import

#rownames(data_ER) = 1:nrow(data_ER)

@@

>>>>

# import questionnaire data from RedCap

data_quest <- read.csv(here("04_RawData", "pilot", "CERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
colnames(data_quest)[1] <- "set" # rename the first column

# remove unnecessary variables from questionnaire data frame

data_quest <- subset(data_quest, select = -c(vl, date, preparatory_coged_complete, general_questions_timestamp, state,
                                            general_questions_complete, inclusion, inclusion_0___1, inclusion_0___2, inclusion_0_2,
                                            researcher_questions_complete, nasatlx_timestamp, nasatlx_complete, t1_psychopy_ed_csv,
                                            t1_psychopy_nback_csv, files_coged_complete, record_id_2, vl_er,
                                            date_er, preparatory_ered_complete, emg_eeg, emg_vhdr, emg_vmrk,
                                            files_ered_complete, followup_ered_timestamp,
                                            nachb_01, nachb_01_inhalt, nachb_02, nachb_02_inhalt, nachb_03, nachb_07, nachb_07_inhalt,
                                            nachb_08, nachb_08_inhalt, nachb_08_haeufig, nachb_08_zurueck, followup_ered_complete,
                                            nfc_timestamp, nfc_complete, bis_11_timestamp, bis_11_complete, bscs_timestamp,
                                            bscs_complete, srs_timestamp, srs_complete, erq_erqse_timestamp, erq_erqse_complete,
                                            who5_timestamp, who5_complete, acs_timestamp, acs_complete, cdrisc_timestamp,
                                            cdrisc_complete, flexer_timestamp, flexer_complete))

@@

## 2.8 Pilot study
